Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-04 acl.2016/acl2016.tex
acl paper

We also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector, $C$ \emph{and} the end position of most recent source word that has been translated, $e$. The distortion limit must be checked for every instance of a hypothesis and translation rule, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $hypo$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
      \IF {can-expand($C(hypo)$, $e(hypo)$, translation rule range)}
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next stack
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}
However, by separating hypotheses into \emph{'ministacks'} according to coverage and end position, the distortion limit only needs to be checked for each ministack, Figure~\ref{algo:Hypothesis Expansion with Sorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $ministack_{C, e}$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
    \IF {can-expand($C$, $e$, translation rule range)}
      \FORALL{ $hypo$ in $ministack_{C, e}$} 
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next ministack
      \ENDFOR
    \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Sorted Stack}
\label{algo:Hypothesis Expansion with Sorted Stack}
\end{figure}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
Table~\ref{tab:stack-configuration} and Figure~\ref{fig:stack-configuration} present the decoding time and average model on the held out test set.
\begin{table}[h]
\tiny
\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|} \hline
Pop-limit	& \multicolumn{2}{c|}{Cardinality}	& \multicolumn{2}{c|}{Coverage}	& \multicolumn{2}{c|}{Coverage \& end pos} \\ \hline
100  		& 73		& -8.64513 		& 75		& -8.64513	& 72	& -8.64513 \\
500		& 237		& -8.59563		& 225		& -8.59563 	& 229	& -8.59612 \\
1,000	 	& 416		& -8.58700		& 397		& -8.58700	& 423	& -8.5870 \\ 
5,000 		& 1930		& -8.58165		& 1931		& -8.58165	& 2153	& -8.58098 \\ 
10,000 		& 3619		& -8.58133		& 3630		& -8.58133	& 4576	& -8.58015 \\ 
15,000 		& 4830		& -8.58130		& 5001		& -8.58130	& 7156	& -8.57999 \\ 
20,000 		& 5849		& -8.58130		& 5916		& -8.58130	& 9583	& -8.57994 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32threads) and average model scores for different stack configurations}
\label{tab:stack-configuration}
\end{table}

>>>>

We also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector, $C$ \emph{and} the end position of most recent source word that has been translated, $e$. The distortion limit must be checked for every instance of a hypothesis and translation rule, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $hypo$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
      \IF {can-expand($C(hypo)$, $e(hypo)$, translation rule range)}
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next stack
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}
However, by separating hypotheses into \emph{'ministacks'} according to coverage and end position, the distortion limit only needs to be checked for each ministack, Figure~\ref{algo:Hypothesis Expansion with Sorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $ministack_{C, e}$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
    \IF {can-expand($C$, $e$, translation rule range)}
      \FORALL{ $hypo$ in $ministack_{C, e}$} 
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next ministack
      \ENDFOR
    \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Sorted Stack}
\label{algo:Hypothesis Expansion with Sorted Stack}
\end{figure}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
Table~\ref{tab:stack-configuration} and Figure~\ref{fig:stack-configuration} present the decoding time and average model on the held out test set.
\begin{table}[h]
\tiny
\begin{center}
\begin{tabular}{|r|r|r|r|r|r|r|} \hline
Pop-limit	& \multicolumn{2}{c|}{Cardinality}	& \multicolumn{2}{c|}{Coverage}	& \multicolumn{2}{c|}{Coverage \& end pos} \\ \hline
		& Time		& Score			& Time		& Score		& Time		& Score	\\ \hline
100  		& 73		& -8.64513 		& 75		& -8.64513	& 72	& -8.64513 \\
500		& 237		& -8.59563		& 225		& -8.59563 	& 229	& -8.59612 \\
1,000	 	& 416		& -8.58700		& 397		& -8.58700	& 423	& -8.5870 \\ 
5,000 		& 1930		& -8.58165		& 1931		& -8.58165	& 2153	& -8.58098 \\ 
10,000 		& 3619		& -8.58133		& 3630		& -8.58133	& 4576	& -8.58015 \\ 
15,000 		& 4830		& -8.58130		& 5001		& -8.58130	& 7156	& -8.57999 \\ 
20,000 		& 5849		& -8.58130		& 5916		& -8.58130	& 9583	& -8.57994 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in secs with 32threads) and average model scores for different stack configurations}
\label{tab:stack-configuration}
\end{table}
